---
title: "Re-analysis of Feit et al. (2016)"
output: html_notebook
---
# ONLY FOR WINDOWS
```{r setup, include = FALSE}
Sys.getenv("PATH")

Sys.setenv(PATH = paste(Sys.getenv("PATH"), 
                        "C:\\RTools40",
                        "C:\\RTools40\\mingw64\\bin", 
                        sep = ";"))
# Did it work (look at the end)?
Sys.getenv("PATH")
```

# Install the following packages. Ensure R version >= 4.00. 
```{r setup, include = FALSE}
#Install the following packages. Ensure R version >= 4.00.install.packages("tidyverse")
install.packages("ggplot2")
install.packages("readxl")
install.packages("openxlsx")
install.packages("Hmisc")
install.packages("modelr")
install.packages("qqplotr")
install.packages("dplyr")
install.packages("ggbeeswarm")
install.packages("broom")
install.packages("car")
```

# Load the following packages with the commands in this block
```{r setup, include = FALSE}
library("Hmisc")
library("tidyverse")
library("ggplot2")
source("R/commons.R") # load functions that are shared across notebooks
library("readxl")
library("openxlsx")
library("modelr")
library("qqplotr")
library("dplyr")
library("ggbeeswarm")
library("broom")
library("car")
```
## Separate text files into different conditions and extract data from questionnaire
- Parse the file names to differentiate between mixed, sentence and random conditions.

*OUTPUT:*
Mixed: list of file names that contain the mixed condition.
Sentence: list of file names that contain the sentence condition.
Random: list of file names that contain the random condition.

- Assign touch typit and non-touch-typist according to the answer in the questionnaire.

*OUTPUT:*
touch_typist_id: a list of user_id strings that are touch typist.
non_touch_typist_id: a list of user_id strings that are non-touch typist.

```{r}
#data_file_paths <- list.files("data", full.names = TRUE)
mixed =list.files("data",pattern="[^(a-zA-Z)]*(Mix)[^(a-zA-Z)]*", full.names = TRUE)
random =list.files("data",pattern="[^(a-zA-Z)]*(Random)[^(a-zA-Z)]*", full.names = TRUE)
sentence =list.files("data",pattern="[^(a-zA-Z)]*(Sentence)[^(a-zA-Z)]*", full.names = TRUE)

# 2 x 1 touch typist
read_xls <- read.xlsx("Background.xlsx")


touch_typist <- which(read_xls$`Do.you.use.the.touch.typing.system.with.all.10.fingers?.If.so,.how.many.years.of.experience.do.you.have?`>= 1)
non_touch_typist <- which(read_xls$`Do.you.use.the.touch.typing.system.with.all.10.fingers?.If.so,.how.many.years.of.experience.do.you.have?`< 1)

touch_typist_id <- read_xls[c(touch_typist),1]
non_touch_typist_id <- read_xls[c(non_touch_typist),1]



#non_touch_typist <- which(read_xls[13] <= 1)
#n <- subset(read_xls, select = c(touch_typist) )

```
# Extract data:
```{r}
i = 0
vars <- c("mixed", "random", "sentence")
for (var in vars){
  i = 0
  for (path in eval(parse(text=var))){
    if (i == 0){
    nam <- paste(var, "mod", sep="_")
    tabcurr <- read.table(file=path, sep="\t", quote="", comment.char="")
    colnames(tabcurr) <- lapply(tabcurr[1, ], as.character)
    tabcurr <- tabcurr[-1,]
    assign(nam, tabcurr)

    }
    else{
    newtab <- read.table(file=path, sep="\t", quote="", comment.char="")
    colnames(newtab) <- lapply(newtab[1, ], as.character)
    newtab <- newtab[-1,]
    chars <- as.character("mixed_mod")

   if (nam[[1]] == as.character("mixed_mod")){
     mixed_mod <- rbind(newtab, mixed_mod)
   } else if (nam[[1]] == as.character("random_mod")){
     random_mod <- rbind(newtab, random_mod)
   } else if (nam[[1]] == as.character("sentence_mod")){
     sentence_mod <- rbind(newtab, sentence_mod)
   }
    
  }
  i <- i + 1
  }
  }

```
# Creating a Dataset with the needed attributes for comparison:

*OUTPUT*
Dataframes with the following names:

NonTouchTypist_mixed_mode
NonTouchTypist_sentence_mode
NonTouchTypist_random_mode

TouchTypist_mixed_mode
TouchTypist_sentence_mode
TouchTypist_random_mode

Including:
user_id, mean_wmp_per_person, mean_sd_iki_per_person, mean_uer_per_person, mean_ke_per_person

```{r}
# typeist/nontypist = response var ahand vo wmp ist wkeit in gruppe von ty or nty so höcht.
sentence_mod <- as.data.frame.matrix(sentence_mod)
mixed_mod <- as.data.frame.matrix(mixed_mod)
random_mod <- as.data.frame.matrix(random_mod)
condition_list <- list(sentence_mod, mixed_mod, random_mod)
names_of_dataframes <- list("sentence_mod", "mixed_mod", "random_mod")
i = 1
for (df in condition_list){
  wmp_nam <- paste(names_of_dataframes[i] , "wmp", sep="_")
  sd_iki_nam <- paste(names_of_dataframes[i] , "sd_iki", sep="_")
  uer_nam <- paste(names_of_dataframes[i] , "uer", sep="_")
    ke_nam <- paste(names_of_dataframes[i] , "ke", sep="_")

  #create one sd_iki per input per person  
  assign(sd_iki_nam, df %>% group_by(user_id, current_input) %>% summarise(mean_iki = mean(as.numeric(sd_iki)))%>% group_by(user_id) %>% summarise(mean_sd_iki= mean(as.numeric(mean_iki))))

#create one wmp per input per person  
  assign(wmp_nam, df %>% group_by(user_id, current_input) %>% summarise(m_wmp = mean(as.numeric(wpm)))%>% group_by(user_id) %>% summarise(mean_wmp= mean(as.numeric(m_wmp))))

  #create one uer per input per person  
  assign(uer_nam, df %>% group_by(user_id, current_input) %>% summarise(m_uer = mean(as.numeric(uer)))%>% group_by(user_id) %>% summarise(mean_uer= mean(as.numeric(m_uer))))

    #create one ke per input per person  
  assign(ke_nam, df %>% group_by(user_id, current_input) %>% summarise(m_ke = mean(as.numeric(ke)))%>% group_by(user_id) %>% summarise(mean_ke= mean(as.numeric(m_ke))))
  
#mean wmp per person  
  print(df)
currnam_wmp <-  df %>% group_by(user_id, current_input) %>% summarise(m = mean(as.numeric(wpm)))%>% group_by(user_id) %>% summarise(mean_wmp_per_person = mean(as.numeric(m)))

#mean sd_iki per person  to use var below
currnam_sd_iki <-  df %>% group_by(user_id, current_input) %>% summarise(m = mean(as.numeric(sd_iki)))%>% group_by(user_id) %>% summarise(mean_sd_iki_per_person = mean(as.numeric(m)))

#mean uer per person to use var below
currnam_uer <-  df %>% group_by(user_id, current_input) %>% summarise(m = mean(as.numeric(uer)))%>% group_by(user_id) %>% summarise(mean_uer_per_person = mean(as.numeric(m)))

#mean ke per person to use var below
currnam_ke <-  df %>% group_by(user_id, current_input) %>% summarise(m = mean(as.numeric(ke)))%>% group_by(user_id) %>% summarise(mean_ke_per_person = mean(as.numeric(m)))

#Separate data set in Touch typist and nontouch typist
tt <- paste("TouchTypist" , names_of_dataframes[i], sep="_")
ntt <- paste("NonTouchTypist" , names_of_dataframes[i], sep="_")

#Assign parts of dataset containing the mean wmp to either touch-typist or non-touch typist
tt_wmp <- currnam_wmp[currnam_wmp$user_id %in% c(touch_typist_id),]
ttsd_iki <- currnam_sd_iki[currnam_sd_iki$user_id %in% c(touch_typist_id),]
tt_uer <-currnam_uer[currnam_uer$user_id %in% c(touch_typist_id),]
tt_ke <-currnam_ke[currnam_ke$user_id %in% c(touch_typist_id),]
ttlist <- list(tt_wmp, ttsd_iki, tt_uer, tt_ke)

#can be extended for the additional attributes
assign(tt, Reduce(
  function(x, y, ...) merge(x, y, ...),
  ttlist
))

#Assign parts of dataset containing the mean of the different measures to either touch-typist or non-touch typist
ntt_wmp <- currnam_wmp[currnam_wmp$user_id %in% c(non_touch_typist_id),]
nttsd_iki <- currnam_sd_iki[currnam_sd_iki$user_id %in% c(non_touch_typist_id),]
ntt_uer <-currnam_uer[currnam_uer$user_id %in% c(non_touch_typist_id),]
ntt_ke <-currnam_ke[currnam_ke$user_id %in% c(non_touch_typist_id),]

nttlist <- list(ntt_wmp, nttsd_iki, ntt_uer, ntt_ke)

assign(ntt, Reduce(
    function(x, y, ...) merge(x, y, ...), 
    nttlist
  )) 
  i <- i + 1
  
}
  # final_df <- assign(ntt, Reduce(
  #   function(x, y, ...) merge(x, y, ...), 
  #   nttlist
  # )) 
  # print(final_df)
  # #filtertt <- t2[t2$user_id %in% c(touch_typist_id),]
  # i <- i + 1
  
#}

```
The bar plots generated from the three data frames - to compare to Figure 3 in the paper
```{r}
#wmp = dv
#variable changed
both <- function(dfNames){
  do.call(rbind, lapply(dfNames, function(x){
    currnam <- substr(x,1, nchar(x)-16)
    cbind(get(x), source = currnam)
  }))
}
conds <- function(dfNames){
  do.call(rbind, lapply(list(dfNames), function(x){
    currnam <- substr(x,1, nchar(x)-5)
    cbind(get(x), cond = currnam)
  }))
}
mixed_both <- both(c("TouchTypist_mixed_mod", "NonTouchTypist_mixed_mod"))
sentence_both <- both(c("TouchTypist_sentence_mod", "NonTouchTypist_sentence_mod"))
random_both <- both(c("TouchTypist_random_mod", "NonTouchTypist_random_mod"))
new <- conds(c("sentence_both", "mixed_both", "random_both"))

```
# Plot residuals with qqplot
lm(attributes ~touchornontouch*condition)
```{r multi_dataset_input, echo = TRUE}


m <- function(attributelist, pl){
models <- lapply(attributelist, function(x){
  curr_plot <- paste("Plot" , x, sep="_")
curr_p <- lm(substitute(i~ source*cond, list(i = as.name(x))), data= new)


curr_lm <- new %>%
  add_residuals(curr_p)

if(pl[1]== 1){
assign(curr_plot, curr_lm %>%
  ggplot(aes(sample = resid)) +
    ggtitle(str_replace_all(curr_plot, "([_])", " "))+
    geom_qq_band(bandType = "ks", mapping = aes(fill = "KS"), alpha = 0.2) +
    geom_qq_band(bandType = "ts", mapping = aes(fill = "TS"), alpha = 0.2) +
    geom_qq_band(bandType = "pointwise", mapping = aes(fill = "Normal"), alpha = 0.2)  +
        geom_qq_band(bandType = "boot", mapping = aes(fill = "Bootstrap"), alpha = 0.2) +
  stat_qq_line(size=.2) +
  stat_qq_point(size = 0.7))
  
}else if(pl[1]== 2){
  summary(curr_p)
  new %>%
    group_by(source) %>%
  mutate(dist_mdn = eval(as.name(x))-mean(eval(as.name(x)))) %>%
    ggplot(aes(x=source, y =dist_mdn, group = source, colour=cond), alpha=0.9)+
    geom_violin(aes(fill=source),colour = "white", alpha = 0.2)+
    geom_beeswarm(size = 2, cex=2, alpha= 0.9)+
    
    stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), 
        geom="errorbar", color="black", width=0.2) +
  stat_summary(fun.y=mean, geom="point", color="black")+
    theme_minimal()
}
else{
assign(curr_plot, ggplot(new, aes(cond, eval(as.name(x)), color=source))
       +stat_smooth(method="glm", formula=substitute(i~ cond, list(i = as.name(x))), alpha=0.2, size = 1, aes(fill=source))+
         geom_point(position=position_jitter(height=0.03, width=0), alpha=0.5)+
         ggtitle(str_replace_all(curr_plot, "([_])", " "))+
         xlab("conditions")+ylab(substr(as.character(x), 6, nchar(as.character(x))-11)))}


})
}
plots <- c("1", "2")
attributelist <- list("mean_wmp_per_person", "mean_sd_iki_per_person", "mean_uer_per_person", "mean_ke_per_person")

#
print(m(attributelist, 1))
print(m(attributelist, 2))
print(m(attributelist, 3))

```
```{r multi_dataset_input, echo = TRUE}
bindf <- new %>%
    mutate(s_fac = factor(source, levels=c("TouchTyp", "NonTouchTyp")),
           prob_t = as.numeric(s_fac)-1
           )

  print(bindf)
  glm_tnt <- glm(s_fac~mean_wmp_per_person, data = bindf, family = binomial(link = "logit"))
  
  
anova_cont <- Anova(glm_tnt, type="II")
coeff_cont <- tidy(glm_tnt, conf.int = TRUE, exponentiate = TRUE)



p_prediction <-
  bindf %>%
  add_predictions(glm_tnt) %>%
  mutate(Prob = plogis(pred)) %>%

  # plotting function
  ggplot(aes(x = mean_wmp_per_person, color = source)) +
  geom_point(aes(y = prob_t)) +
  geom_line(aes(y = Prob), color = "blue") +
  xlab("words per minute")+
  ylab("Probability of being a Touch Typist") +
  theme(legend.position = "none")
print(p_prediction)

```


# Plots of all conditions per group
for each condition a plot comparing touch and nontouch typist for all the different metrics.
```{r multi_dataset_input, echo = TRUE}
datalist <- list(sentence_both, mixed_both, random_both)
cond <- list("sentence_both", "mixed_both", "random_both")
i = 1
condition_model <- vector("list", 3)
for (df in datalist){
curr_mod <- paste("model", i, sep="_")
print(i)
condition_model[[curr_mod]] <- lapply(attributelist, function(x){
curr_lm <- lm(substitute(i~ source, list(i = as.name(x))), data=df)


summary(curr_lm)
#df.predict <- cbind(df, predict(attributelist[i], interval='confidence'))
p <- ggplot(data = df, aes_string(x = "source", y = x)) + 
  geom_point(color='blue')+
  ggtitle(as.character(cond[[i]]))

assign(curr_mod,p + stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), 
        geom="errorbar", color="red", width=0.2) +
  stat_summary(fun.y=mean, geom="point", color="red"))
})
i = i+1
}
print(condition_model)
# sentence_lm <- lm(mean_wmp_per_person ~ source, data= sentence_both)
# print(summary(sentence_lm))
# 
# p <- ggplot(data = sentence_both, aes(x = source, y = mean_wmp_per_person)) + 
#   geom_point(color='blue')
# p + stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), 
#         geom="errorbar", color="red", width=0.2) +
#   stat_summary(fun.y=mean, geom="point", color="red")

```
random
```{r multi_dataset_input, echo = TRUE}
# random_lm <- lm(mean_wmp_per_person ~ source, data= random_both)
# print(summary(random_lm))
# 
# p <- ggplot(data = random_both, aes(x = source, y = mean_wmp_per_person)) + 
#   geom_point(color='blue')
# p + stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), 
#         geom="errorbar", color="red", width=0.2) +
#   stat_summary(fun.y=mean, geom="point", color="red")

```
mixed:
# ```{r multi_dataset_input, echo = TRUE}
# mixed_lm <- lm(mean_wmp_per_person ~ source, data= mixed_both)
# print(summary(mixed_lm))
# 
# p <- ggplot(data = mixed_both, aes(x = source, y = mean_wmp_per_person)) + 
#   geom_point(color='blue')
# p + stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), 
#         geom="errorbar", color="red", width=0.2) +
#   stat_summary(fun.y=mean, geom="point", color="red")

```

__Answer:__
<!-- ```{r multi_dataset_answer, echo = TRUE} -->
<!-- md_answer <-  -->
<!--   md_input + -->
<!--   geom_point(stat="summary", fun.y = "mean", color="red", shape="diamond", size=5, position=position_nudge(x = 0.18))+ -->
<!--   geom_errorbar(stat="summary", fun.data="mean_se", fun.args=list(mult=1.96), color = "blue", position=position_nudge(x=0.18), width=0) -->
<!-- md_answer -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # generate bar plots for all 3 dfs -->
<!-- # for mixed -->
<!-- # ggplot(condition_list[[1]], aes(as.numeric(wpm))) + geom_bar() -->
<!-- # # for random -->
<!-- # ggplot(condition_list[[2]], aes(as.numeric(wpm))) + geom_bar() -->
<!-- # # for sentence -->
<!-- # ggplot(condition_list[[3]], aes(as.numeric(wpm))) + geom_bar() -->

<!-- # generate bar plots for all 3 dfs for touch-typists -->
<!-- # for mixed -->
<!-- ggplot(condition_list[[1]] %>% filter(user_id %in% touch_typist_id), aes(as.numeric(wpm))) + geom_bar() -->
<!-- # for random -->
<!-- ggplot(condition_list[[2]] %>% filter(user_id %in% touch_typist_id), aes(as.numeric(wpm))) + geom_bar() -->
<!-- # for sentence -->
<!-- ggplot(condition_list[[3]] %>% filter(user_id %in% touch_typist_id), aes(as.numeric(wpm))) + geom_bar() -->

<!-- # generate bar plots for all 3 dfs for non touch-typists -->
<!-- # for mixed -->
<!-- ggplot(condition_list[[1]] %>% filter(user_id %in% non_touch_typist_id), aes(as.numeric(wpm))) + geom_bar() -->
<!-- # for random -->
<!-- ggplot(condition_list[[2]] %>% filter(user_id %in% non_touch_typist_id), aes(as.numeric(wpm))) + geom_bar() -->
<!-- # for sentence -->
<!-- ggplot(condition_list[[3]] %>% filter(user_id %in% non_touch_typist_id), aes(as.numeric(wpm))) + geom_bar() -->
<!-- ``` -->
