---
title: "Re-analysis of Feit et al. (2016)"
output: html_notebook
---

```{r setup, include = FALSE}
library(tidyverse)
source("R/commons.R") # load functions that are shared across notebooks
library("readxl")
library("openxlsx")
```

## Separate text fils into different conditions and extract data from questionnaire
- parse the file names to differentiate between mixed, sentence and random conditions.

*OUTPUT*
mixed: list of file names that contain the mixed codition
sentence: list of file names that contain the sentence codition
random: list of file names that contain the random codition

- Assign touch typit and non-touch-typist according to the answer in the questionnaire:

*OUTPUT*
touch_typist_id: a list of user_id strings that are touch typist
non_touch_typist_id: a list of user_id strings that are non-touch typist


```{r}
#data_file_paths <- list.files("data", full.names = TRUE)
mixed =list.files("data",pattern="[^(a-zA-Z)]*(Mix)[^(a-zA-Z)]*", full.names = TRUE)
random =list.files("data",pattern="[^(a-zA-Z)]*(Random)[^(a-zA-Z)]*", full.names = TRUE)
sentence =list.files("data",pattern="[^(a-zA-Z)]*(Sentence)[^(a-zA-Z)]*", full.names = TRUE)

# 2 x 1 touch typist
read_xls <- read.xlsx("Background.xlsx")


touch_typist <- which(read_xls$`Do.you.use.the.touch.typing.system.with.all.10.fingers?.If.so,.how.many.years.of.experience.do.you.have?`>= 1)
non_touch_typist <- which(read_xls$`Do.you.use.the.touch.typing.system.with.all.10.fingers?.If.so,.how.many.years.of.experience.do.you.have?`< 1)

touch_typist_id <- read_xls[c(touch_typist),1]
non_touch_typist_id <- read_xls[c(non_touch_typist),1]



#non_touch_typist <- which(read_xls[13] <= 1)
#n <- subset(read_xls, select = c(touch_typist) )

```
##Extract data:
```{r}
i = 0
vars <- c("mixed", "random", "sentence")
for (var in vars){
  i = 0
  for (path in eval(parse(text=var))){
    if (i == 0){
    nam <- paste(var, "mod", sep="_")
    tabcurr <- read.table(file=path, sep="\t", quote="", comment.char="")
    colnames(tabcurr) <- lapply(tabcurr[1, ], as.character)
    tabcurr <- tabcurr[-1,]
    assign(nam, tabcurr)

    }
    else{
    newtab <- read.table(file=path, sep="\t", quote="", comment.char="")
    colnames(newtab) <- lapply(newtab[1, ], as.character)
    newtab <- newtab[-1,]
    chars <- as.character("mixed_mod")

   if (nam[[1]] == as.character("mixed_mod")){
     mixed_mod <- rbind(newtab, mixed_mod)
   } else if (nam[[1]] == as.character("random_mod")){
     random_mod <- rbind(newtab, random_mod)
   } else if (nam[[1]] == as.character("sentence_mod")){
     sentence_mod <- rbind(newtab, sentence_mod)
   }
    
  }
  i <- i + 1
  }
  }

```
##Creating a Dataset with the needed attributes for comparison:

*OUTPUT*
Dataframes with the following names:

NonTouchTypist_mixed_mode
NonTouchTypist_sentence_mode
NonTouchTypist_random_mode

TouchTypist_mixed_mode
TouchTypist_sentence_mode
TouchTypist_random_mode

Including:
user_id, mean_wmp_per_person, mean_sd_iki_per_person, mean_uer_per_person, mean_ke_per_person

```{r}
# typeist/nontypist = response var ahand vo wmp ist wkeit in gruppe von ty or nty so höcht.
sentence_mod <- as.data.frame.matrix(sentence_mod)
mixed_mod <- as.data.frame.matrix(mixed_mod)
random_mod <- as.data.frame.matrix(random_mod)
condition_list <- list(sentence_mod, mixed_mod, random_mod)
names_of_dataframes <- list("sentence_mod", "mixed_mod", "random_mod")
i = 1
for (df in condition_list){
  wmp_nam <- paste(names_of_dataframes[i] , "wmp", sep="_")
  sd_iki_nam <- paste(names_of_dataframes[i] , "sd_iki", sep="_")
  uer_nam <- paste(names_of_dataframes[i] , "uer", sep="_")
    ke_nam <- paste(names_of_dataframes[i] , "ke", sep="_")

  #create one sd_iki per input per person  
  assign(sd_iki_nam, df %>% group_by(user_id, current_input) %>% summarise(mean_iki = mean(as.numeric(sd_iki)))%>% group_by(user_id) %>% summarise(mean_sd_iki= mean(as.numeric(mean_iki))))

#create one wmp per input per person  
  assign(wmp_nam, df %>% group_by(user_id, current_input) %>% summarise(m_wmp = mean(as.numeric(wpm)))%>% group_by(user_id) %>% summarise(mean_wmp= mean(as.numeric(m_wmp))))

  #create one uer per input per person  
  assign(uer_nam, df %>% group_by(user_id, current_input) %>% summarise(m_uer = mean(as.numeric(uer)))%>% group_by(user_id) %>% summarise(mean_uer= mean(as.numeric(m_uer))))

    #create one ke per input per person  
  assign(ke_nam, df %>% group_by(user_id, current_input) %>% summarise(m_ke = mean(as.numeric(ke)))%>% group_by(user_id) %>% summarise(mean_ke= mean(as.numeric(m_ke))))
  
#mean wmp per person  
  print(df)
currnam_wmp <-  df %>% group_by(user_id, current_input) %>% summarise(m = mean(as.numeric(wpm)))%>% group_by(user_id) %>% summarise(mean_wmp_per_person = mean(as.numeric(m)))

#mean sd_iki per person  to use var below
currnam_sd_iki <-  df %>% group_by(user_id, current_input) %>% summarise(m = mean(as.numeric(sd_iki)))%>% group_by(user_id) %>% summarise(mean_sd_iki_per_person = mean(as.numeric(m)))

#mean uer per person to use var below
currnam_uer <-  df %>% group_by(user_id, current_input) %>% summarise(m = mean(as.numeric(uer)))%>% group_by(user_id) %>% summarise(mean_uer_per_person = mean(as.numeric(m)))

#mean ke per person to use var below
currnam_ke <-  df %>% group_by(user_id, current_input) %>% summarise(m = mean(as.numeric(ke)))%>% group_by(user_id) %>% summarise(mean_ke_per_person = mean(as.numeric(m)))

#Separate data set in Touch typist and nontouch typist
tt <- paste("TouchTypist" , names_of_dataframes[i], sep="_")
ntt <- paste("NonTouchTypist" , names_of_dataframes[i], sep="_")

#Assign parts of dataset containing the mean wmp to either touch-typist or non-touch typist
tt_wmp <- currnam_wmp[currnam_wmp$user_id %in% c(touch_typist_id),]
ttsd_iki <- currnam_sd_iki[currnam_sd_iki$user_id %in% c(touch_typist_id),]
tt_uer <-currnam_uer[currnam_uer$user_id %in% c(touch_typist_id),]
tt_ke <-currnam_ke[currnam_ke$user_id %in% c(touch_typist_id),]
ttlist <- list(tt_wmp, ttsd_iki, tt_uer, tt_ke)

#can be extended for the additional attributes
assign(tt, Reduce(
  function(x, y, ...) merge(x, y, ...),
  ttlist
))

#Assign parts of dataset containing the mean of the different measures to either touch-typist or non-touch typist
ntt_wmp <- currnam_wmp[currnam_wmp$user_id %in% c(non_touch_typist_id),]
nttsd_iki <- currnam_sd_iki[currnam_sd_iki$user_id %in% c(non_touch_typist_id),]
ntt_uer <-currnam_uer[currnam_uer$user_id %in% c(non_touch_typist_id),]
ntt_ke <-currnam_ke[currnam_ke$user_id %in% c(non_touch_typist_id),]

nttlist <- list(ntt_wmp, nttsd_iki, ntt_uer, ntt_ke)


 assign(ntt, Reduce(
  function(x, y, ...) merge(x, y, ...), 
  nttlist
)) 
#filtertt <- t2[t2$user_id %in% c(touch_typist_id),]
  i <- i + 1
  
}
```